Considering scale in multilayer animal social networks

### 2020-06-28 paper/manuscript.Rmd
drop specific dates time results

The temporal multilayer network indicated within-year time windows where social 
network metrics increased. Edge overlap was higher in time windows 1, 6-11 and 
15-20 (between `r timedefs[timecut == 1, paste(mindate, maxdate, sep = ' and ')]`,
`r timedefs[timecut %in% 6:11, paste(min(mindate), max(maxdate), sep = ' and ')]`
and `r timedefs[timecut %in% 15:20, paste(min(mindate), max(maxdate), sep = ' and ')]`)
than in time windows 2-5 and 12-15 (between 
`r timedefs[timecut %in% 2:5, paste(min(mindate), max(maxdate), sep = ' and ')]`
and `r timedefs[timecut %in% 12:15, paste(min(mindate), max(maxdate), sep = ' and ')]`)
(Figure \@ref(fig:temp) A). Time windows of higher edge overlap, between 
approximately October and June, also had higher graph strength 
compared to time windows of lower edge overlap, between approximately June 
and October (Figure \@ref(fig:temp) C). Graph strength peaked across the time 
series between  
`r timedefs[timecut %in% 9:10, paste(min(mindate), max(maxdate), sep = ' and ')]`. 
These results suggest that ordinal multilayer networks can effectively 
capture discrete time windows of aggregation and dissaggregation related 
to resource availability, and highlight the importance of carefully 
selecting the temporal scale of analysis. <!-- TODO see comment-->

>>>>

The temporal multilayer network indicated within-year time windows where social 
network metrics increased. Edge overlap was higher in time windows 1, 6-11 and 
15-20 than in time windows 2-5 and 12-15 
(Figure \@ref(fig:temp) A). Time windows of higher edge overlap, between 
approximately October and June, also had higher graph strength 
compared to time windows of lower edge overlap, between approximately June 
and October (Figure \@ref(fig:temp) C). Graph strength peaked across the time 
series between January 2018 and April 2018. 
These results suggest that ordinal multilayer networks can effectively 
capture discrete time windows of aggregation and dissaggregation related 
to resource availability, and highlight the importance of carefully 
selecting the temporal scale of analysis. <!-- TODO see comment-->
